x---
title: "إBalad data set"
output: html_notebook
---


Loding data:
```{r}
df <- read.csv("C:/Users/Ultra/Desktop/balad/submit_actions.csv")
df <-data.frame(df)
typeof(df)
head(df)
```



Removing Duplicates:
```{r}
## removing duplicates
df_2 <- df[,c(2,3,4,5,6,7,8,9)]
df <- df[ !duplicated(df_2),]
df <- df[order(df$device_id,df$created_at),]
head(df)
## obviosly we can not remove duplicates
```









-------------------------------- Data wrangling ---------------

Here I am rying to find order of actions  each user made to identify master patterns
by this mean I am adding some axillary fields:


STATE :     adding a key column to label each records of user, cotaining:
            START       :   it can be "Edit"  or "New". we identify begininh of the Pocess
            Net Err     :   when user action is  "NEXT" or "PRE"  but real "next page" field  is not changing. i take it as Net Err
            Field Err   :   when page is null and action is "Error". 
            DONE/UNDONE :   End of the process
            1-2-3       :   in case non of the above options are valid, and row is simply a transition to next page, then we take "next page" as stat. 
            
next_page   :     showing the page user was in.

* fisrt we need to sort data by device_id ,  created_at

```{r}

df$action_code <- 0
df$stat <- ''

df$page_number <- as.numeric(df$page_number)

df$action_code <- ifelse(df$action =='submit_next_page', +1,df$action_code)
df$action_code <- ifelse(df$action =='submit_prev_page',-1,df$action_code)
df$stat <- ifelse(df$action =='enter_submit' & df$is_form_edit =="false",'New 1'   ,df$stat)
df$stat <- ifelse(df$action =='enter_submit' & df$is_form_edit =="true",'Edit 1'   ,df$stat)
df$stat <- ifelse(df$action =='exit_submit'  & df$is_successful =="true",'done'  ,df$stat)
df$stat <- ifelse(df$action =='exit_submit'  & df$is_successful =="false",'undone',df$stat)

head(df)
library(dplyr)
df$next_page <- as.numeric(lead(df$page_number, n = 1))
# df$next_field_name <-lead(df$field_name, n = 1)


df$stat <- ifelse(df$action_code !=0 & (df$page_number + df$action_code) != df$next_page  , paste('NetErr',df$next_page),df$stat  )
df$stat <- ifelse(df$action_code !=0 & (df$page_number + df$action_code) == df$next_page  , paste(df$next_page),df$stat  )

df$stat <- ifelse( is.na(df$page_number) ,df$next_page ,df$stat)
df$stat <- ifelse( is.na(df$next_page) , paste('Field Err[',df$next_field_name ,']')  ,df$stat)

df$stat <- ifelse( is.na(df$page_number) &!is.na(df$next_page)  , df$next_page,df$stat)


df[order(df$device_id,df$created_at),][450:460,c(2,3,5,7:12)]
df[order(df$device_id,df$created_at),][450:580,c(3,11)]

df[1:30,]

str(df)



```








Pivoting all the stats of a user form "Stat" point of his Journey to the "End" point.
Containing all he did and experienced.
Each elemnt of the list, is chain actions of a sub.

```{r}

find_user_loop <- function(test){
    loops <- ''
    loop<-''
    for( i in 1: nrow( test)){
          if(test[i,]$stat == 'New 1' | test[i,]$stat == 'Edit 1' ){
              loop<- append( as.character(test[i,]$device_id) , test[i,]$stat) 
              # print(as.character(test[i,]$device_id)
                  
          }else if(   grepl('done' , test[i,]$stat) ){
              loop<- append( loop , test[i,]$stat)
              loops <- c(loops, list(loop))
              # print(loop)
            
          }else {
              loop<- append( loop , test[i,]$stat)
          }
    }
    return (loops)
}



# 
# test <- df[df$device_id=='-08pnnHRTr2Ui7rU03GJ3w' | df$device_id == '-09dv6gUTOeNxKS7g_zCoQ',]
# test
# loop_test <-find_user_loop(test)
# loop_test


loops <-find_user_loop(df)
loops
head(loops)
test$stat
grepl('done' , 'undone')
```






We want to check, how many chain actions does a user do?
chain actions : is set of actions, having an start point, and an end point
# Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 1.000   4.000   5.000   5.301   6.000 199.000 

*result : 75% of subs, having at most 6 actions on they chain, befor they finish.
* maximum actions done by a user = 199
* generally  248.751  user chain actions are identified. 


```{r}


loops
cols_cnt <- sapply(loops,nrow)
cols_cnt
loop_size_all <- sapply(loops,FUN = NROW)
summary(loop_size_all)
max(loop_size_all,decreasing = TRUE)#[1000:2000]       

# Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 1.000   4.000   5.000   5.301   6.000 199.000 
# max number of action a used have made
# Loop size= 75%   6

sort(loop_size_all,decreasing = TRUE)#[1000:2000]
hist(loop_size_all,main = "distribution of actions cnts, in a chain")

NROW(loop_size_all)  #248.751
loop_size = 199
loop_size

```


let's zoom on cnts below 10:
Mod= 3 actions:
Start ->  0   ->  Done
```{r}
hist(loop_size_all[loop_size_all<10],main = "distribution of actions cnts, in a chain ( magnified)")


```
which distribution does it blong to?
it is not logaritmic

```{r}
hist(log(loop_size_all),main = "distribution of actions cnts, in a chain ( magnified)")


```
trying to transform this count and making it Normal, but bot even close. Boxcox failed

```{r}
library(forecast)
lambda <- BoxCox.lambda(loop_size_all)
loop_size_all_transformed <- scale(BoxCox(loop_size_all,lambda))
hist(loop_size_all_transformed,main="transformed loop_size_all")
lambda  #-0.9999381

```




To work easily with this chain actions, we need to transform this list of lists, into a dataframe.
Here we select each col of supper list and feed it into a data.frame.
```{r}



v <- unlist ( lapply(loops, '[', 1) )
head(v)
df.loops <- data.frame(v)
# df.loops
head(df.loops)
loop_size=199
for(i in 2:loop_size){
  v <- unlist ( lapply(loops, '[', i) )
  df.loops <- cbind(df.loops , v)
  print(head(v))
}
head(df.loops)

names(df.loops) <-c("device_id" ,"v1", "v2","v3","v4","v5","v6","v7","v8","v9","v10"
                                ,"v11","v12","v13","v14","v15","v16","v17","v18","v19","v20"
                                ,"v21","v22","v23","v24","v25","v26","v27","v28","v29","v30"
                                ,"v31","v32","v33","v34","v35","v36","v37","v38","v39","v40"
                                ,"v41","v42","v43","v44","v45","v46","v47","v48","v49","v50"
                                ,"v51","v52","v53","v54","v55","v56","v57","v58","v59","v60"
                                ,"v61","v62","v63","v64","v65","v66","v67","v68","v69","v70"
                                ,"v71","v72","v73","v74","v75","v76","v77","v78","v79","v80"
                                ,"v81","v82","v83","v84","v85","v86","v87","v88","v89","v90"
                                ,"v91","v92","v93","v94","v95","v96","v97","v98","v99","v100"
                                ,"v101","v102","v103","v104","v105","v106","v107","v108","v109","v110"
                                ,"v111","v112","v113","v114","v115","v116","v117","v118","v119","v120"
                                ,"v121","v122","v123","v124","v125","v126","v127","v128","v129","v130"
                                ,"v131","v132","v133","v134","v135","v136","v137","v138","v139","v140"
                                ,"v141","v142","v143","v144","v145","v146","v147","v148","v149","v150"
                                ,"v151","v152","v153","v154","v155","v156","v157","v158","v159","v160"
                                ,"v161","v162","v163","v164","v165","v166","v167","v168","v169","v170"
                                ,"v171","v172","v173","v174","v175","v176","v177","v178","v179","v180"
                                ,"v181","v182","v183","v184","v185","v186","v187","v188","v189","v190"
                                ,"v191","v192","v193","v194","v195","v196","v197","v198"
)

head(df.loops)


```







Adding some practical summary features to dataset.
* while analyzing, this fields are added  pace by pace and not all at once.

result      :  1: when chain is finished by "Done"
               2: when chain is finished by "undone"  
               
page_sum    :  sum of all the pages, user had visited. ex: visiting  2->3->2->3  will result  in 10. This field is used as a code.
               while,there are just some few top templates which will be revealed later
               5: visiting 2 ->3
               8: 2->3->2->1   
               8: 2->3->2->3  
               0: visting page 1 and simply leaving the process
               
page_cnt    :  How many pages has the user visited in total?

field_err_cnt: How many Field Error does user face in his/her session or chain?
Net_err_cnt :  How many Network Error does user face in his/her session or chain?
               
EF_xxxxx    :  How many Field Error of type xxxxx did user face?           

```{r}


df.loops[100:110,1:6]
df.loops$result <- 0
df.loops$page_sum <-0
df.loops$page_cnt <-0


df.loops$result        <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (x=='done',1,0),na.rm = TRUE) )

df.loops$field_err_cnt <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('Field Err' , x),1,0),na.rm = TRUE) )
df.loops$Net_err_cnt   <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('NetErr' , x),1,0),na.rm = TRUE) )

df.loops$FE_brand      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('brand' , x),1,0),na.rm = TRUE) )
df.loops$FE_brand_model<-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('brand_model' , x),1,0),na.rm = TRUE) )
df.loops$FE_category   <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('category' , x),1,0),na.rm = TRUE) )
df.loops$FE_description      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('description' , x),1,0),na.rm = TRUE) )
df.loops$FE_link       <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('link' , x),1,0),na.rm = TRUE) )
df.loops$FE_location   <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('location' , x),1,0),na.rm = TRUE) )
df.loops$FE_national_id      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('national_id' , x),1,0),na.rm = TRUE) )
df.loops$FE_new_credit <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('new_credit' , x),1,0),na.rm = TRUE) )
df.loops$FE_new_price  <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('new_price' , x),1,0),na.rm = TRUE) )
df.loops$FE_phone      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('phone' , x),1,0),na.rm = TRUE) )
df.loops$FE_post_type  <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('post_type' , x),1,0),na.rm = TRUE) )
df.loops$FE_rooms      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('rooms' , x),1,0),na.rm = TRUE) )
df.loops$FE_simcard_type      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('simcard_type' , x),1,0),na.rm = TRUE) )
df.loops$FE_size       <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('size' , x),1,0),na.rm = TRUE) )
df.loops$FE_title      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('title' , x),1,0),na.rm = TRUE) )
df.loops$FE_type       <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('type' , x),1,0),na.rm = TRUE) )
df.loops$FE_usage      <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('usage' , x),1,0),na.rm = TRUE) )
df.loops$FE_user_type  <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('user_type' , x),1,0),na.rm = TRUE) )
df.loops$FE_year       <-apply(df.loops,MARGIN = 1, function(x) sum(ifelse (grepl('year' , x),1,0),na.rm = TRUE) )

df.loops$FE_type

df.loops$page_sum      <-apply(df.loops[,1:199],MARGIN = 1, function(x) sum(ifelse(  !is.na(as.numeric(as.character.numeric_version(x)))  ,as.numeric(as.character.numeric_version(x)),0)  , na.rm = TRUE)) 
hdf.loops$page_cnt      <-apply(df.loops[1:10,1:199],MARGIN = 1, function(x) sum(ifelse(  !is.na(as.numeric(as.character.numeric_version(x)))  ,1,0)  , na.rm = TRUE)) 
df.loops$page_sum 


df.loops$page_sum      <- apply(df.loops[1:10,1:199],MARGIN = 1, function(x) sum(ifelse(  !is.na(as.numeric(as.character.numeric_version(x)))  ,as.numeric(as.character.numeric_version(x)),0)  , na.rm = TRUE)) 


test<-df.loops[1:100,1:199]
test
 apply(test[1:10,1:199] ,MARGIN = 1, function(x) sum(ifelse(  !is.na(as.numeric(as.character.numeric_version(x)))  ,as.numeric(as.character.numeric_version(x)),0)  , na.rm = TRUE))

df.loops$page_sum 

head(df.loops[109,1:199])
df.loops[df.loops$is_back_Forth_user_user + df.loops$is_classic_wizzard_user + df.loops$is_to_zero == 0,]
ncol(df.loops)
df.loops[1:20, c(3:8,200:225)]


```




#-------------------------  conversion rate  -------------------------  
*  Total conversion rate:
   121316  / (121316 + 125630)  = 49%

```{r}

library(dplyr)

# perform this condition to filter out noise. this guys have no start point

######  Total conversion rate:
df.loops %>%
  filter(result<=1)%>%
  group_by(result) %>%
  summarise(
    cnt = n()
  ) %>%
  arrange(desc(cnt)) 
```


######  conversion rate  based on Edit and New use cases:

# Edit Page Conversion rate:  66302  / (93056 + 66302)  = 41%
# New  Page Conversion rate:  55014  / (55014 + 32573)  = 62%
```{r}
df.loops %>%
  filter(result<=1 & !is.na(result)) %>%
  group_by(v1,result) %>%
  summarise(
    cnt = n()
  ) %>%
  arrange(desc(cnt)) 

```
















# -----------------------------------------------------------------------------------------  
#---------------------------------                       -----------------------------------  
#---------------------------------  Answering Questions  -----------------------------------
#---------------------------------                       -----------------------------------  
# -----------------------------------------------------------------------------------------  
# does NetErro effect result?
# does Field Error Effect the result?
# what is in common between poeple who are are undone?














Here I  come up with top available patterns. 
I call them with a name
and try to identifysimilarities:
# result  v2,                v3,                v4,                 v5                 v6                  v7                   page_cnt  page_sum   cnt
# 1      0 0     undone                                                                                 1        0 75960   #--0--- to zero
# 2      1 NetErr 1     2            3            done                                                  2        5 37990   #--1---classic wizar
# 3      0 NetErr 0     undone                                                                          0        0  9666   #--0--- to zero
# 4      1 2            3            done                                                               2        5  8893   #--1---classic wizar
# 5      1 NetErr 1     Field Err    2            3            done                                     2        5  2526   #--1---classic wizar
# 6      1 NetErr 1     2            1            2            3            done                        4        8  1559   #--1---back and forth 
# 7      1 NetErr 1     NetErr 1     2            3            done                                     2        5  1204   #--1---classic wizar
# 8      1 Field Err    2            3            done                                                  2        5  1084   #--1---classic wizar
# 9      1 2            1            NetErr 1     2            3            done                        4        8  1052   #--1---back and forth 
# 10     0 2            1            0            undone                                                3        3   863   #--0--- to zero
# 11     0 undone                                                                                       0        0   763   #--0--- to zero
# 12     1 2            1            2            3           done                                      4        8   681   #--1---back and forth 
# 13     0 NetErr 1     2            1            0           undone                                    3        3   609   #--0--- to zero
# 14     1 Field Err          Field Err          1            2            3            done            3        6   608   #--1---classic wizar
# 15     0 NetErr 1     2            3           2            1            0                            5        8   589   #--1---back and forth 
# 16     1 NetErr 1     2            3           2            1            2                            6       13   565   #--1---back and forth 
# 17     1 NetErr 1     Field Err          Field Err          2            3            done            2        5   509   #--1---classic wizar
# 18     0 0            undone       Field Err          Field Err          1            0               3        1   502   #--0--- to zero
# 19     1 NetErr 1     2            1            NetErr 1     2           3                            4        8   465   #--1---back and forth 
# 20     0 2            3            2            1            0           undone                       5        8   459   #--0--- to zero
# 21     0 2            3            2            1            0           undone                       5        8   457
# 22     1 NetErr 1     2            3            2            3           done                         4       10   388
# 23     0 0            undone       0            undone                                                2        0   356   #--0--- to zero
# 24     1 Field Err    Field Err    2            3            done                                     2        5   321
# 25     1 Field Err    1            2            3            done                                     3        6   316
# 26     0 NetErr 1     0            undone                                                             1        0   251   #--0--- to zero
# 27     1 Field Err    Field Err    1            Field Err    2            3                           3        6   236
# 28     1 0            undone       Field Err    1            NetErr 1     2                           4        6   223
# 29     1 Field Err    Field Err    Field Err    2            3            done                        2        5   180
# 30     1 NetErr 1     NetErr 1     NetErr 1     2            3            done                        2        5   171


####################################################################################
Here we label 3 types of usage. and we identify a rule to destinguish each :       #
                                                                                   #
1.Classic Wizzard                                                                  #
  Definition:                                                                      #
  users who are simply passing wizzard steps 1 by 1.                               #
  1 -> 2 -> 3                                                                      #
  Characteristic:                                                                  #
  They are usually end up  successfully                                            #
  rule:                                                                            #
     page_cnt  = 2   &&  page_sum = 0    ==                                        #
                         page_sum = 6    ==>  classic wizzard                      #
                                                                                   #
                                                                                   #
2.Back and Forth                                                                   #
  Definition:                                                                      #
  users who are not following the wizzard. they wondering between pages            #
  Characteristic:                                                                  #
  1 -> 2 -> 3 ->2 ->1 : most likely to result in fialur and leaving the process    #
  1 -> 2 -> 3 ->2 ->3 : most likely to end up successfully                         #
  rule:                                                                            #
                         page_sum>= 8   ==>  back and forth                        #
                                                                                   #
                                                                                   #
3. to zero                                                                         #
  Definition:                                                                      # 
  This users might never visit page 3                                              #
  Characteristic:                                                                  #
  They mostly result in fialur and leaving the process                             #
                     page_sum <=1    ==                                            #
  page_cnt  = 3   &&  page_sum = 3    == >  to zero                                #
                                                                                   #                                                         
* usage_pattern: 1:to zero1   2:Classic Wizzard  3:Back and Forth                  #
####################################################################################
                                                                                   #
  From This results find  out that                                                 #
  1. those who come back to 0,  leave the process undone                           # 
  2. Those who back and forth and stop by Page#3   finish successfully             #
  3. Those who back and forth and stop by Page#0   leave undone                    #
  4. those who follow thi wizzard are more likely to finish the successfully       #
                                                                                   #
####################################################################################




```{r}
library(dplyr)
res1<- df.loops %>%
  filter(v1=='New 1') %>%
  group_by(result,substr(v2,1,9),substr(v3,1,9),substr(v4,1,9),substr(v5,1,9),substr(v6,1,9),substr(v7,1,9),substr(v8,1,9),substr(v9,1,9),page_cnt,page_sum ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange(desc(cnt))
nrow(res1)  #1153
res1[1:20,]
```



Now that we find out about these 3 groups
let's lable uers with 

```{r}

df.loops$is_classic_wizzard_user <- ifelse((df.loops$page_cnt == 2   &  df.loops$page_sum == 5) | ( df.loops$page_sum == 6) ,1 ,0)
df.loops$is_back_Forth_user_user <- ifelse(   df.loops$page_sum >= 8 ,1,0)
df.loops$is_to_zero <- ifelse( (df.loops$page_sum <=1) |  (df.loops$page_cnt  == 3   &  df.loops$page_sum == 3) ,1,0)

df.loops$usage_pattern <- -1

df.loops$usage_pattern <- ifelse(   df.loops$is_to_zero ==1 ,0,df.loops$usage_pattern)
df.loops$usage_pattern <- ifelse(   df.loops$is_classic_wizzard_user ==1 ,1,df.loops$usage_pattern)
df.loops$usage_pattern <- ifelse(   df.loops$is_back_Forth_user_user ==1 ,2,df.loops$usage_pattern)


ncol(df.loops)
```




















Q: How does  page_cnt effect the result?
* page count is 1 unit less that reallity bczof programming style. that means wee need to add 1 to this measure. page_cnt = 0 means one page is seen.

A: visting less than 1 page, can result in failur
# p(page_cnt<=1 | succuss):  (131 + 138) / (10641 + 131+ 76849 +138 )  =   0.3 %
but
# p(page_cnt>=2 | succuss):  (131 + 138) / (10641 + 131+ 76849 +138 )  =  92.9 %

```{r}
library(dplyr)

res1<- df.loops %>%
  filter(v1=='New 1' & result<=1) %>%
  group_by(result,page_cnt ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange(page_cnt)
nrow(res1)  #39
res1[1:40,]

# p(page_cnt>=2 | succuss):  (54437 + 2347 + 6527 + 434 + 1687 + 101) / (759 + 54437+ 2607 +2347+ 121 + 6527 + 434+ 1521 + 1687+ 101)  =  0.3 %


```


```{r}

library(ggplot2)
 ggplot(data = res1 ,aes( x=page_cnt , y = cnt,fill = as.factor(result) ))+
   geom_bar(stat = "identity",position = position_dodge())


```



```{r}

 res1<- df.loops %>%
   filter(v1=='New 1' & result<=1) %>%
   group_by(result,page_sum,page_cnt) %>%
   summarise(
     cnt = n()
   )  %>%
   arrange(desc(cnt))
 nrow(res1)  #39
 res1[1:40,]
 
```



----------------------------------------  Network Error Assessment-------------------------------------------------





Q :Does Net Error impact the resutl?
A : Total number is different. but is there significantly different?
```{r}

summary(df.loops$Net_err_cnt)
is_page_sum_lt_3

res1<- df.loops %>%
  filter(v1=='New 1' & result<=1 & Net_err_cnt<10 ) %>%
  # group_by(result,  is_page_sum_lt_3 =  ifelse(page_sum>=5,1,0)  , net_er_level = round(Net_err_cnt/3,0)) %>%
  group_by( page_sum  , net_er_level = ifelse(Net_err_cnt>=1,1,0)) %>%
  
  summarise(
    cnt = n()
  )  %>%
  arrange(desc(cnt))
nrow(res1)  #2
res1#[1:2,]

```




desc:  We need to assess that with chi-square. But se should transform it first, since chi-square works with Normal Distibution
A:   p-value = 1  shows that there is not significance interaction between "Net_err_cnt"  and "result"


```{r}
t <- log(table(df.loops$Net_err_cnt ,df.loops$result ) +1)
t
chisq.test( t   )

```




Q: Does network Error Effect visited pages?

```{r}


res1<- df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  # group_by(result,  is_page_sum_lt_3 =  ifelse(page_sum<=3,1,0)  , net_er_level = round(Net_err_cnt/3,0)) %>%
  group_by(  page_sum  , net_er_level = ifelse(Net_err_cnt>1,1,0) ) %>%
  # group_by( page_sum ) %>%
  
  summarise(
    cnt = n()
  )  %>%
  arrange(page_sum)
nrow(res1)  #140
res1#[1:20,]

```


```{r}


library(ggplot2)
 ggplot(data = res1 ,aes( x=page_sum , y = log(cnt) ,fill = as.factor(net_er_level) ))+
   geom_bar(stat = "identity",position = position_dodge())

 
```


desc:  We need to assess that with chi-square. But se should transform it first, since chi-square works with Normal Distibution
A:   p-value = 1  shows that there is not significance interaction between "Net_err_cnt"  and "page_sum"


```{r}
t <- log(table( df.loops$page_sum , ifelse(df.loops$Net_err_cnt>1,1,0) ) +1)
t
chisq.test( t   )

```



```{r}


res1<- df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  # group_by(result,  is_page_sum_lt_3 =  ifelse(page_sum<=3,1,0)  , net_er_level = round(Net_err_cnt/3,0)) %>%
  group_by(  is_page_sum_gt_5 =  ifelse(page_sum>=5,1,0)   , net_er_level = ifelse(Net_err_cnt>1,1,0) ) %>%
  # group_by( page_sum ) %>%
  
  summarise(
    cnt = n()
  )  %>%
  arrange(net_er_level)
nrow(res1)  #140
res1#[1:20,]

```



A: Errors does not preventusers from going through the process. users visiting more pages, experiencing even more Net Error.

* lets Just remember that majority of people are stoping at page 1
```{r}

library(ggplot2)
 ggplot(data = res1 ,aes( x=is_page_sum_gt_5 , y = cnt ,fill = as.factor(net_er_level) ))+
   geom_bar(stat = "identity",position = position_dodge())


```



```{r}

res1<- df.loops %>%
  filter(v1=='New 1' & result<=1 & Net_err_cnt<10 ) %>%
  # group_by(result,  is_page_sum_lt_3 =  ifelse(page_sum>=5,1,0)  , net_er_level = round(Net_err_cnt/3,0)) %>%
  group_by( result  , net_er_level = ifelse(Net_err_cnt>=1,1,0)) %>%
  
  summarise(
    cnt = n()
  )  %>%
  arrange(net_er_level)
nrow(res1)  #63
res1

```







# ###############################################
# Now the Question is:
# why people do not go furthur from page 1 or 2?
# does Network Err or field Error play any role?

```{r}




summary(df.loops$Net_err_cnt)
is_page_sum_lt_3

res1<- df.loops %>%
  filter(v1=='New 1' & result<=1 & Net_err_cnt<10 ) %>%
  # group_by(result,  is_page_sum_lt_3 =  ifelse(page_sum>=5,1,0)  , net_er_level = round(Net_err_cnt/3,0)) %>%
  group_by(result,  is_page_sum_lt_3 =  ifelse(page_sum>=5,1,0)  , net_er_level = ifelse(Net_err_cnt>=1,1,0)) %>%
  
  summarise(
    cnt = n()
  )  %>%
  arrange(net_er_level,is_page_sum_lt_3)
nrow(res1)  #63
res1[1:20,]
####  Majority of failaur cases stop at page 0 for no reason. It s a routine  case in marketing data. this people are just trying options of the page.
####  lets ignor this group
#
#
# result is_page_sum_lt_3 net_er_level   cnt
# 1      0                0            0 79505
# 2      1                0            0   169
# 3      0                1            0   829
# 4      1                1            0 14870
# 5      0                0            1 11571   *
# 6      1                0            1   145   *
# 7      0                1            1  1142   *
# 8      1                1            1 51117   *
ggplot(data = res1 ,aes( x=Net_err_cnt , y = cnt,fill = as.factor(result) ))+
  geom_bar(stat = "identity",position = position_dodge())+
  geom_text( aes( label = Net_err_cnt))


```











----------------------------------    fixing the rule of "patterns"    --------------------------------------



```{r}


# setting labels:  cheking miss identifications. trying to check  rules of patterns

library(dplyr)
names(df.loops)
res1<- df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  # group_by(result,is_page_sum_gt_3 =  ifelse(page_sum>=5,1,0)
  # ,  FE_category ) %>%
  group_by(result ,page_cnt,page_sum,is_classic_wizzard_user,is_back_Forth_user_user,is_to_zero ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange( desc(cnt))
nrow(res1)  #63
res1


```






getting to know this three groups statistically:


   is_classic_wizzard_user        57497 / (57497+199)   = 99.6 % sucessfull 
   is_back_Forth_user_user        7960  / (1701 +7960 ) = 82.3 % sucessfull  ==>  when page_cnt = 4 then success  -   when page_cnt=5 then fialur
   is_to_zero                     90724 / (90724+171)   = 99.8 % failur




when the visit is like:        1 ->                           the chance ofbeing succefull is like:1 -( (90724 +171 )   /( 171+ 90724 + 674 + 432 +7960+ 1701 + 57497 + 199) ) = 0.4296176%

when he reachs page 2 and 3:   1 -> 2 -> 3 ->                 it will be so probable to success   (57497 + 7960+ 1701) /( 674 + 432 +7960+ 1701 + 57497 + 199)  = 98% chance to get succusfull

if he comes back to 2:         1 -> 2 -> 3  ->  2 ...>1            there is      1701 / (1701+7960)= 17% chance that he chooses 1 in next step  and the process finishes undon

if he comes back to 2:         1 -> 2 -> 3  ->  2 ...>3            there is      7960 / (1701+7960)= 82% chance that he chooses 3 in next finishs the process succesfully



```{r}


library(dplyr)

names(df.loops)
res1<- df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  # group_by(result,is_page_sum_gt_3 =  ifelse(page_sum>=5,1,0)
           # ,  FE_category ) %>%
  group_by(result,is_classic_wizzard_user,is_back_Forth_user_user,is_to_zero ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange( is_classic_wizzard_user,is_back_Forth_user_user,is_to_zero)
nrow(res1)  #63
res1




```








----------------------------------------  Field Error Assessment-------------------------------------------------


######################################################################################  
# Here I am testing all error counts, against the "result" to see which type
#  in case FE_brand  happens but page >=5 then susscess full.
#
# below error types are looking more effective amoung others:

# row  result      is_page_sum_gt_3  FE_?   cnt
# FE_location:
# 5      1                1          1  4383
# 6      0                0          1   133
# 7      0                1          1   105
# 8      1                0          1     4
#  4383
# FE_category:------------------------------
# 5      1                1          1  1861
# 6      0                0          1    84
# 7      0                1          1    68
# FE_description:---------------------------
# 5      1                1          1   992
# 6      0                0          1   892
# 7      0                1          1    68
# 8      1                0          1     4
# 9      1                1          2   142
# 10     0                0          2   140
# 11     0                1          2    25
# 12     0                0          3    73
# 13     1                1          3    56
# 14     0                1          3     5
# FE_title-----------------------------------
# 5      1                1          1   940
# 6      0                0          1   827
# 7      0                1          1    53
# 8      1                0          1     2
# 9      1                1          2   185
# 10     0                0          2   112
# 11     0                1          2    15
# 12     1                1          3    94
# 13     0                0          3    75
# 14     0                1          3     8
# 15     1                1          4    49
# 16     0                0          4    44
# 17     0                1          4     3
#
#
#
#
# Result:
#  Below fields can effect user, and stop him by page  1 or 2
#  FE_location
#  FE_category
#  FE_description
#  FE_title




```{r}


# "FE_brand"        "FE_post_type"    "FE_user_type"   
# [208] "FE_location"     "FE_usage"        "FE_category"     "FE_description"  "FE_year"         "FE_simcard_type" "FE_size"         "FE_brand_model"  "FE_new_price"   
# [217] "FE_national_id"  "FE_rooms"        "FE_type"         "FE_phone"        "FE_link"         "FE_new_credit"   "FE_title"  

######### field Error type  role in page_sum and result
library(dplyr)
names(df.loops)
res1<- df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  group_by(result,is_page_sum_gt_3 =  ifelse(page_sum>=5,1,0),  FE_category ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange( FE_category ,desc(cnt))
nrow(res1)  #63
res1[1:20,]



```







Q : is there any relationship between Network Error and usage_pattern?
A:  As previously showed, Network Error emerged so high in rate, for users  who visited more pages.
    for sure it can not be an abstacle

```{r}



 df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  group_by(usage_pattern,net_er_level = ifelse(Net_err_cnt>=1,1,0)   ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange( desc(cnt)) %>%
  ggplot(aes( x=usage_pattern , y = cnt,fill = as.factor(net_er_level) ))+
   geom_bar(stat = "identity",position = position_dodge())



```


Q : is there any relationship between Field Error and usage_pattern?
A :  It does not significantly show any causuality relationship. 
     in segment#2 (Classical_wizzard_users), which are 99% successful, we can see most field Errors.
     They can not be taken as any obstacle.

```{r}

 df.loops %>%
  filter(v1=='New 1' & result<=1  ) %>%
  group_by(usage_pattern, has_field_err = ifelse(field_err_cnt>=1,1,0)   ) %>%
  summarise(
    cnt = n()
  )  %>%
  arrange( desc(cnt)) %>%
  ggplot(aes( x=usage_pattern , y = cnt,fill = as.factor(has_field_err) ))+
   geom_bar(stat = "identity",position = position_dodge())
```

























#################################################################################################################
#################################################################################################################
# lets test logetic regression to find out which factors play a role in finishing the job successfully
#
# 1. how does factors effect result?
# 2. how does factors obstacle user in page 0?
# 3. how does factors obstacle user in 1-2-3-2 to comebacke to page 1?

# how does factors effect result?




Q:  how does factors effect result?
A:  it gives us no new information but  seeing more pages can increase the chance of success.
    + most important combinations of success are:
      page_sum5:page_cnt2
      page_sum6:page_cnt3
      page_sum6:page_cnt4
      page_sum8:page_cnt4
    + most important combinations of failur are: 
      page_sum0:page_cnt0
      page_sum0:page_cnt1
      page_sum2:page_cnt1
      page_sum1:page_cnt2
      page_sum3:page_cnt2
      page_sum1:page_cnt3
      page_sum6:page_cnt5
    which we already segmented as Usage_pattern  

```{r}



df.loops.gl <- df.loops[df.loops$result<=1 ,]
df.loops.gl
mdl_result1 <- glm(result ~ field_err_cnt +  page_sum + page_cnt + Net_err_cnt, data = df.loops.gl, family = "binomial")
summary(mdl_result1)

df.loops.gl$page_sum    <-    factor (ifelse(  df.loops.gl$page_sum<=8 , df.loops.gl$page_sum,10))
df.loops.gl$page_cnt    <-    factor( ifelse(  df.loops.gl$page_cnt<=5 , df.loops.gl$page_cnt,10) )
df.loops.gl$Net_err_cnt <-    factor( ifelse(  df.loops.gl$Net_err_cnt>0 , 1,0) )
df.loops.gl$field_err_cnt <-    factor( ifelse(  df.loops.gl$field_err_cnt>0 , 1,0) )
head(df.loops.gl)

##### it gives us no new information but  seeing morepages can increase the chance of success




df.loops.gl <- df.loops[df.loops$result<=1,]
df.loops.gl
mdl_result1 <- glm(result ~ field_err_cnt +  page_sum:page_cnt +  Net_err_cnt, data = df.loops.gl, family = "binomial")
summary(mdl_result1)


```








############################  important result

Q. How does field Errors effect user to be "is_to_zero"  segment?

A. by testing filed and its intraction on page_cnt, we highlight that, below filed, negatively effect user,
   put him/her in "to_zero" serment, 
   and stops him/her from going furthur in the wizzard
   
# page_cnt2:FE_description1    8.041e+00  5.985e-01  13.435  < 2e-16 ***
# page_cnt2:FE_title1          8.706e+00  7.209e-01  12.076  < 2e-16 ***

```{r}

df.loops.gl$page_sum
df.loops.gl <- df.loops[df.loops$result<=1,]
df.loops.gl
df.loops.gl$page_sum    <-    factor (ifelse(  df.loops.gl$page_sum<=6 , df.loops.gl$page_sum,10))
df.loops.gl$page_cnt    <-    factor( ifelse(  df.loops.gl$page_cnt<=5 , df.loops.gl$page_cnt,10) )
df.loops.gl$Net_err_cnt <-    factor( ifelse(  df.loops.gl$Net_err_cnt>0 , 1,0) )
df.loops.gl$FE_brand <-    factor( ifelse(  df.loops.gl$FE_brand>0 , 1,0) )
df.loops.gl$FE_post_type <-    factor( ifelse(  df.loops.gl$FE_post_type>0 , 1,0) )
df.loops.gl$FE_user_type <-    factor( ifelse(  df.loops.gl$FE_user_type>0 , 1,0) )
df.loops.gl$FE_location <-    factor( ifelse(  df.loops.gl$FE_location>0 , 1,0) )
df.loops.gl$FE_usage <-    factor( ifelse(  df.loops.gl$FE_usage>0 , 1,0) )
df.loops.gl$FE_category <-    factor( ifelse(  df.loops.gl$FE_category>0 , 1,0) )
df.loops.gl$FE_description <-    factor( ifelse(  df.loops.gl$FE_description>0 , 1,0) )
df.loops.gl$FE_year <-    factor( ifelse(  df.loops.gl$FE_year>0 , 1,0) )
df.loops.gl$FE_simcard_type <-    factor( ifelse(  df.loops.gl$FE_simcard_type>0 , 1,0) )
df.loops.gl$FE_size <-    factor( ifelse(  df.loops.gl$FE_size>0 , 1,0) )
df.loops.gl$FE_brand_model <-    factor( ifelse(  df.loops.gl$FE_brand_model>0 , 1,0) )
df.loops.gl$FE_new_price <-    factor( ifelse(  df.loops.gl$FE_new_price>0 , 1,0) )
df.loops.gl$FE_national_id <-    factor( ifelse(  df.loops.gl$FE_national_id>0 , 1,0) )
df.loops.gl$FE_rooms <-    factor( ifelse(  df.loops.gl$FE_rooms>0 , 1,0) )
df.loops.gl$FE_type <-    factor( ifelse(  df.loops.gl$FE_type>0 , 1,0) )
df.loops.gl$FE_phone <-    factor( ifelse(  df.loops.gl$FE_phone>0 , 1,0) )
df.loops.gl$FE_link <-    factor( ifelse(  df.loops.gl$FE_link>0 , 1,0) )
df.loops.gl$FE_new_credit <-    factor( ifelse(  df.loops.gl$FE_new_credit>0 , 1,0) )
df.loops.gl$FE_title <-    factor( ifelse(  df.loops.gl$FE_title>0 , 1,0) )



mdl_result1_factor <- glm(is_to_zero ~ FE_brand:page_cnt +FE_brand_model:page_cnt + FE_category:page_cnt
                          + FE_category:page_cnt +   FE_description:page_cnt +FE_link:page_cnt +       FE_location:page_cnt+  FE_national_id:page_cnt + FE_new_credit:page_cnt  +  FE_new_price:page_cnt +   FE_phone:page_cnt
                          + FE_post_type:page_cnt + FE_rooms:page_cnt 
                          +       FE_simcard_type:page_cnt  + FE_size:page_cnt  +        FE_title:page_cnt
                          +       FE_type:page_cnt
                          + FE_usage
                          +       FE_user_type +   FE_year
                          , data = df.loops.gl, family = "binomial")

summary(mdl_result1_factor)
```



```{r}
mdl_result1_factor <- glm(result ~ FE_brand:page_cnt +FE_brand_model:page_cnt + FE_category:page_cnt
                          + FE_category:page_cnt +   FE_description:page_cnt +FE_link:page_cnt +       FE_location:page_cnt+  FE_national_id:page_cnt + FE_new_credit:page_cnt  +  FE_new_price:page_cnt +   FE_phone:page_cnt
                          + FE_post_type:page_cnt + FE_rooms:page_cnt 
                          +       FE_simcard_type:page_cnt  + FE_size:page_cnt  +        FE_title:page_cnt
                          +       FE_type:page_cnt
                          + FE_usage
                          +       FE_user_type +   FE_year
                          , data = df.loops.gl, family = "binomial")

summary(mdl_result1_factor)
```






######################################################################################################################
######################################################################################################################
#################################################   Conclusion  ######################################################
######################################################################################################################
######################################################################################################################
There are 3 patterns which users follow.


   is_classic_wizzard_user        57497 / (57497+199)   = 99.6 % sucessfull 
   is_back_Forth_user_user        7960  / (1701 +7960 ) = 82.3 % sucessfull  ==>  when page_cnt = 4 then success  -   when page_cnt=5 then fialur
   is_to_zero                     90724 / (90724+171)   = 99.8 % failur


is_classic_wizzard_user reaches page 2 and 3
is_back_Forth_user_user reaches 2 and 3 and wonders around. If he gets backe to page 1, there is a high chance that he/she might fails
                        but if she/he gets backe to page 3, most probably she/he will successfully finish the chain.
is_to_zero              never reaches page 3 and sometimes even page 2 ( this is the most common case)


so:
1. what makes people stock  on first pages and do no proceed to next page?
   sometimes they are just trying "Add advertise" butt
   or
   sometimes, based on logestic regression, there are some fileds, that significiantly, increase the chance of being in "is_to_zero" segment.
   Description  +  title
   errors on this field increase the chance of being in "is_to_zero" segment, therefor decrease the chance of visiting other pages,
   that is capstone of ending unsuccessfully.
   on the other hand, there are some fileds on age 3, which attract usere to click on finish and submite the advertisment.
   we need to make user visit that page faster. As I tried this dunction on Divar App, I found out page 3, includes lots of "Selection Components".
   They are easy to fill, and attractive for user. But Title and Descrption textboxs, are hard  to fill. It's hard for android user to fill it.
   I guess users give up, when they see this 2 big textboxes and they miss fantastic multi-selection components of page3.
   
   
   suggestion:
   what if you put Description and Title Textboxs on page 3, and show users attractive multi-selection components first?
   they are easy to fill out, and when user reach Desciption and Title and very last page, he/she would more likely fill the boxs, cause that's the last       step.He wont give up whole process now, while he has already filled a lot. that would be a wast to quite at page 3.
   
2.What makes people reach page 3, come backe to page 2, but never get back to the wizzard fot page 3 agian?
   I did not have enough time to answer this question
   but there are 20% of  "is_back_Forth_user_user" segment, that we lose on this regard.



